% vim: set tw=78 sts=2 sw=2 ts=8 aw et ai:

\subsection{Fat binary scenarios}

The user might first want to find out if a binary file is fat (or universal)
and then extract the code for a specific archtecture in order to obtain a
standalone executable for a single architecture.

\subsection{Entitlement scenarios}

An attacker would try to craft a malicious executable which would be useless
without an entitlement signature, therefore the attacker would need to insert
a new signature to validate the malicious entitlement. This feature would
enable the user to extract an entitlement signature from the binary in order
to validate it.

\subsection{Library cache scenarios}

In order to gain more information about a given binary we could inspect the
API calls to a dynamic library that the binary is to be dynamically linked
with. Knowing what library function the binary calls might help us in finding
security breaches.

\subsection{Sandbox profile binary extraction scenarios}

The sandbox profile binaries should be extracted in order to be further
processed by SandBlaster to reverse the sandbox profiles. The end goal here is
to escape the application sandbox

\subsection{Dump syscall table scenarios}

During binary file analysis we would identify what system calls the
application makes. Because of the closed nature of the kernel we do not know
what system calls are being made, so we need to extract the system call table
in order to find this out. This way we can further investigate entry points
into the kernel
